Quantum Computing and its Implications on Digital Security

### 2021-12-12 paper.tex
feat: Improve ion trap

There is not a single way to build a quantum computer. 
Instead, different approaches can be followed to develop machines utilizing quantum effects for computing. Some of which will be discussed in the following section.

@@

There are different attempts of realizations of quantum computers.
Those different approaches have different advantantages and challenges. 
Some of those realizations, especially the ones important with regards to digital security, 
are summarized in the following:

\begin{subsection}{Ion Traps}
The ion trap quantum computer encodes data in energy states of ions and in vibrational modes between ions. 
Conceptually, each ion is operated by a sepearte laser. 
A preliminary analysis demonstrated that Fourier transforms can be evaluated with the ion trap computer. 
This, in turn, leads to Shor's factoring algorithm, 
which is based on Fourier transforms.

Also refered to as "trapped ion quantum computer". 
The fundamental operations of a quantum computer have been demonstrated experimentally with the currently highest accuracy in trapped ion systems. 
Trapped ion computers are researched because they could be used for a large-scale quantum computer.
Scaling the ion trap to a large number of qubits could be accomplished by combining multiple ion traps into an array and transporting ions between them. 
As of 2018, the largest number of particles to be controllable entangled is 20 trapped ions. 
In 2021, researchers from the University of Innsbruck presented a quantum computing demonstrator that fits inside two 19-inch server racks, 
the world's first qualirt standards meeting compact trapped ion quantum computer.

Challenges for ion traps include initialization of the ion's motional states, 
the relatively brief lifetimes of the photon states and the decoherence which is is caused when the qubits interact with the external environment undesirably.
\end{subsection}

>>>>

There is not a single way to build a quantum computer. 
Instead, different approaches can be followed to develop machines utilizing quantum effects for computing. Some of which will be discussed in the following section.
\end{section}

@@

There are different approaches to realize quantum computers.
Those different approaches have different advantantages and challenges. 
Some of those realizations, especially the ones important with regards to digital security, 
are summarized in the following:

\begin{subsection}{Ion Traps}
Vedral and Plenio describe the workings of the ion trap in their paper \cite{2008} as follows. 
They state that the ion trap quantum computer represents qubits in energy states and in vibrational modes between ions. 
In a linear ion trap, currents in electrodes generate a time dependent electric field. 
Ions then move through this potential and for some currents and ion masses, the ions get trapped in the field. 
The equilibrium is caused by the force from the electric field generated by the electrodes and the electrostatic repulsion of the ions. 
The ions form a string seperated by only a few wavelengths of light. 
The distance of a few wavelengths is sufficient to operate each ion with a different laser. 
A challenge the researchers faced when trying to realize an ion trap is the mechanical degree of freedom the ions have. 
In general, the ions are trapped at their position but they are in fact not resting but oscillating around their equilibrium position. 
The ions then get cooled by using laser cooling to reduce the movement of the ions in their current position. 
This process is able to cool down the ions near 0 Kelvin. 
At this point, the only movement left would be the movement caused by the quantum mechanical uncertainty priciple. 
So far, it is not possible to cool a whole string of ions to near 0 K, 
although several attempts cooling down a single ion and two ions succeeded.

As mentioned by Prashant in his paper \cite{prashant}, it has been possible to evaluate Fourier transforms using the ion trap quantum computer.
This achievment lead to Shor's factoring algorithm, 
which is based on performing Fourier transforms.

The ion trap could demonstrate the fundamental operations of a quantum computer with the highest accuracy so far. 
Ion trap quantum computers are researched because they could potentially be used for a large-scale quantum computer as scaling the ion trap to a large number of qubits could be accomplished by combining multiple ion traps into an array. Ions then could be transported between the ions traps. 
As of 2018, the largest number of particles to be controllable entangled is 20 trapped ions. 
In 2021, scientists from the University of Innsbruck presented a quantum computer based on the ion trap that fits inside two 19-inch server racks.
\end{subsection}
